\documentclass{article}
\usepackage{graphicx} % Required for inserting images

\usepackage[utf8]{inputenc}

\usepackage{amsmath,amsthm, amssymb}
\usepackage[margin=3cm]{geometry}
\usepackage{mathtools}
\usepackage{dsfont}
\usepackage{xcolor}
\usepackage{algorithm,algpseudocode}
\usepackage{todonotes}
\usepackage{nicefrac}
\usepackage{mathrsfs}
\usepackage{tikz}

\usepackage{hyperref}


\tikzstyle{arrow} = [thick,->,>=stealth]

\usepackage{thm-restate}

\usepackage{etoc}

\usepackage{setspace}
% \setstretch{1.125}


%%%%%%%%    THEOREM DEFINITIONS AND RESTATABLE
% \newcounter{claim}
% \setcounter{claim}{0}
\newtheorem{theorem}{Theorem}
\newtheorem{lemma}[theorem]{Lemma}
\newtheorem{corollary}[theorem]{Corollary}
% \newtheorem{claim}[theorem]{Claim}
\newtheorem{definition}{Definition}
\newtheorem{prop}{Proposition}
\newtheorem{assumption}{Assumption}

\usepackage{todonotes}

\newcommand{\matt}[1]{\todo[color=red!50, prepend, caption={Matt}, tickmarkheight=0.25cm]{#1}}
\newcommand{\note}[1]{\emph{Note: #1}}
\newcommand{\conjecture}[1]{ \noindent\emph{\textbf{Conjecture:}} \emph{ #1 }}
\DeclareMathOperator{\Tr}{Tr}

\usepackage{amsthm}

%%%%%%%%    NOTATION DEFINITIONS FOR EASIER WRITING
\newcommand{\ket}[1]{|#1\rangle}
\newcommand{\bra}[1]{\langle #1|}
\newcommand{\braket}[2]{\langle #1|#2\rangle}
\newcommand{\ketbra}[2]{| #1\rangle\! \langle #2|}
\newcommand{\parens}[1]{\left( #1 \right)}
\newcommand{\brackets}[1]{\left[ #1 \right]}
\newcommand{\abs}[1]{\left| #1 \right|}
\newcommand{\norm}[1]{\left| \left| #1 \right| \right|}
\newcommand{\diamondnorm}[1]{\left| \left| #1 \right| \right|_\diamond}
\newcommand{\anglebrackets}[1]{\left< #1 \right>}
\newcommand{\overlap}[2]{\anglebrackets{#1 , #2 }}
\newcommand{\set}[1]{\left\{ #1 \right\}}
\newcommand{\divides}{\bigm|}
\newcommand{\ceil}[1]{\left\lceil #1 \right\rceil}
\newcommand{\openone}{\mathds{1}}
\newcommand{\expect}[1]{\mathbb{E}\brackets{#1}}
\newcommand{\variance}[1]{\textit{Var} \brackets{ #1 }}
\newcommand{\prob}[1]{\text{Pr}\left[ #1 \right]}
\newcommand{\bigo}[1]{O\left( #1 \right)}
\newcommand{\bigotilde}[1]{\widetilde{O} \left( #1 \right)}
\newcommand{\ts}{\textsuperscript}

\newcommand{\trace}[1]{\Tr \brackets{ #1 }}
\newcommand{\partrace}[2]{\Tr_{#1} \brackets{ #2 }}
\newcommand{\complex}{\mathbb{C}}

%%%%% COMMONLY USED OBJECTS
\newcommand{\hilb}{\mathcal{H}}
\newcommand{\partfun}{\mathcal{Z}}
\newcommand{\identity}{\mathds{1}}
\newcommand{\gue}{\rm GUE}
\DeclareMathOperator{\sinc}{sinc}
\DeclareMathOperator{\hermMathOp}{Herm}
\DeclareMathOperator{\im}{Im}
\newcommand{\herm}[1]{\hermMathOp\parens{#1}}



\title{Interpreting Multipartite Entanglement through Topological Summaries}
\author{Raghav Banka, Matthew Hagan, Nathan Wiebe}
\date{October 2023}

\begin{document}

\maketitle

\section{Introduction}
Entanglement is a hallmark feature of quantum mechanics and allows for correlations between separated systems that go beyond those allowable through classical mechanics. Although the presence of entanglement itself does not represent any kind of advantage over classical computation or communication, when entanglement is present with operations restrictions, such as only allowing arbitrary \emph{local} operations and classical communication (LOCC) between subsystems, then entanglement can become a resource. In the simulation of quantum matter, such as the electronic structure problem in chemistry or finding ground states of condensed matter systems, highly entangled ground states can pose a barrier to classical computers. Despite this importance, our understanding of entanglement is mostly based on bipartite entanglement, or quantum correlations between two halves of a single quantum state. As many quantum systems tend to have more than two constituent parties recently efforts have been made to provide an analysis for multipartite entanglement \cite{horodecki2024multipartiteentanglement}. 

\textcolor{red}{\textbf{Multipartite entanglement paragraph here.}}

In a seemingly unrelated area of research, mathematicians and computer scientists have developed analytical tools based on topology to provide insights into structural characteristics of datasets. These techniques, which fall under the umbrella term of Topological Data Analysis (TDA), gives an overview of how many ``holes" are present in a dataset across varying distance scales. The canonical example is if we have samples of coordinates from a 3-dimensional surface it would be nice to know if the samples come from a sphere compared to a torus. TDA generalizes spheres vs tori to higher dimensions and provides a robust analysis of the number of holes across distance scales to get an idea of what features are persistent in the dataset as opposed to transient noise. Further, TDA provides a single numerical summary of the underlying manifold that data is sampled from to give a topologically invariant quantity to the data, known as the Euler's Characteristic. In graphs this corresponds to the number of edges minus the number of vertices and in three dimensional shapes it is the number of edges minus the number of vertices and minus the number of faces. This gives a quick necessary heuristic to tell if two shapes or graphs are topologically equivalent but is not sufficient to declare they are indeed the same. 

Recently Hamilton and Leditzky \cite{hamilton2023probing} showed that TDA serves as a mathematically consistent framework for studying multipartite entanglement. They showed that various entropy functionals, such as the Tsallis $q$-deformed entropy, can be used to build simplicial complexes (higher dimensional analogs of graphs) that can be fed into the TDA pipeline. One of their main results is that the resulting Euler Characteristic is exactly equal to a previously used multipartite entanglement measure known as the $n$-tangle. This not only gives a more mathematically sound justification for the use of the $n$-tangle, which was later championed in \cite{horodecki2024multipartiteentanglement} and specifically the 3-tangle, but because the Euler Characteristic is a blunt summary there remains plenty of useful topological information in the TDA pipeline. 

In this paper we continue these efforts at providing mathematically rigorous interpretations to multipartite entanglement through TDA with the goal of providing operational interpretations to the topological information. For example, in bipartite entanglement theory the entropy of entanglement between two subsystems tells us the minimum fidelity of a teleportation protocol that can be carried out between the two, or the number of bell pairs that would be needed to prepare a given bipartite state. In Section \ref{sec:prelims} we give all the necessary mathematical background and notation needed for applying TDA to multipartite quantum states. As for concrete interpretations we give operational meaning for both the Euler Characteristic as well as a characterizing result for the more fine-grained barcode data. In Section \ref{sec:distillable_entanglement} we show that the Euler Characteristic provides an upper and lower bound on the average distillable entanglement between any random bipartition of a quantum state, which can be seen as the average quantum information that can be teleported between randomly chosen parties. In Section \ref{sec:graph_states} we then analyze the barcodes that result from graph states, a fundamental primitive used in quantum communication theory and measurement based quantum computing \cite{nielsen2006} under the name of cluster states. We show that the graph state of a star graph, which is unitarily equivalent to the GHZ state, has a distinct barcode pattern. We further show that \emph{any} quantum state with such a barcode must have come from such a graph state. This shows that the GHZ state has a distinct topological fingerprint, and could be used for future verification protocols. 
 
\section{Preliminaries}\label{sec:prelims}


We study multipartite quantum systems over a Hilbert space $\hilb_A = \hilb_{1} \otimes \hilb_{2} \otimes \ldots \otimes \hilb_{n}$, where for simplicity we will assume each individual quantum system is a qubit $\hilb_{i} = \mathbb{C}^{2}$. We will work with pure states over the total Hilbert space $\hilb_A$ or $\hilb$, denoted $\rho_A = \ketbra{\psi}{\psi}$. The reduced density operator defined over a subset $J \subseteq A$ is equal to the partial trace $\rho_J = \partrace{J^C}{\rho_A}$, where $J^C = A \setminus J$. If necessary, we let $Pos(\hilb_J) \coloneqq \set{X: \hilb_J \to \hilb_J | x^\dagger X x \geq 0 ~\forall x \in \hilb_J}$ denote the set of positive semidefinite operators on a Hilbert space $H_J$ and $D(\hilb_J) \coloneqq \set{\rho \in Pos(\hilb_J) | \trace{\rho} = 1}$ the respective density operators. 

We will primarily be concerned with entropic properties, both linear and logarithmic, of reduced density operators. The standard entropy used for quantum states is the von Neumann entropy $S(\sigma) = - \trace{\sigma \log \sigma}$, where the $\log$ denotes the matrix logarithm. This matrix logarithm is fairly unwieldy to use both in practice and analytically, so we will make heavy use of either the Tsallis entropy or the Renyi divergence instead. The Tsallis entropies are defined for a non-zero real number $q \neq 1$ and are given by
\begin{equation}
    S_{q}(A)_{\rho} = \frac{1}{1 - q} (\trace{\rho_A^q} - 1).
\end{equation}
For $q=2$ the Tsallis entropy is equal to the purity of the state (defined as $1 - \trace{\rho^2}$) and in the limit as $q \to 1$ we have $\lim_{q \to 1} S_q(A)_{\rho} = S(\rho)$. 

We now introduce entanglement, focusing first on the bipartite case and mentioning a few key results in the multipartite scenario. Bipartite entanglement is a key feature of quantum mechanics and relies on a quantum state $\rho$ defined over a two party Hilbert space $\hilb = \hilb_A \otimes \hilb_B$. To define entangled states we first will describe what states are \emph{not} entangled, so-called separable states which are defined as all possible tensor products $\sigma\otimes \tau$, where $\sigma$ and $\tau$ are both valid density operators over $\hilb_A$ and $\hilb_B$ respectively. A state which is not a convex combination, or probabilistic mixture, of separable states is said to be entangled. The key notion is that a convex combination of separable states can be described as classical correlations between registers, which can be built via local unitaries performed separately on each space and classical communication between two operators of $\hilb_A$ and $\hilb_B$. A key quantity for bipartite entanglement is the entropy of entanglement, defined as $S(\rho_A) = S(\rho_B) = -\trace{\rho_B \log \rho_B}$, where $\rho_B = \partrace{\hilb_A}{\rho}$. The reason that this is a useful quantity to consider is that if $\rho$ is a pure state over the total Hilbert space $\hilb_A \otimes \hilb_B$, then the entropy of entanglement is zero if and only if the (pure!) state is separable. 

Multipartite entanglement on the other hand is very much less studied and there are much more nuanced quantities that can be defined. 

\subsection{Topology Data Analysis and Notation}

Topological Data Analysis (TDA) is a set of techniques for investigating properties of datasets related to their topology, or the underlying structure that the datapoints are drawn from. The purpose behind using topology is that the topology of a space is robust to continuous changes of the space, which when applied to data analysis means that the results drawn from TDA should be robust to significant sources of noise. TDA is of interest to the Quantum Computing community for two reasons. The predominant reason is the existence of fast quantum algorithms where no comparable classical algorithms are known. The regime for provable quantum advantages in TDA is an active area of research. The relatively recent application of TDA to quantum computing and information sciences is in revealing a link between computed topological quantities, namely the integrated Betti number, and entropic quantities of underlying quantum states on which TDA is performed. This connection between multipartite entanglement and topological data analysis is the area we explore here. 

To understand the impact of TDA on multipartite entanglement we first need to set our notation for the data we will be analyzing and the topological structures we will be using. We need a sequence of vector spaces, $X^{(i)}$, with maps between them, $\partial_k : X^{(k)} \to X^{(k - 1)}$. The maps $\partial_k$ are referred to as boundary operators, for reasons related to geometry which are explained in Section \ref{sec:simplicial_defs}. Currently the spaces $X^{(i)}$ should be considered as arbitrary vector spaces, later on we will give specific ones that we will use throughout. This collection of vector spaces and maps is a chain complex, written as
\begin{equation}
    X^{(n)} \xrightarrow{\partial_n} X^{(n-1)} \xrightarrow{\partial_{n-1}} \ldots X^{(1)} \xrightarrow{\partial_1} X^{(0)} \xrightarrow{\partial_0} 0,
\end{equation}
if we also enforce the homology condition: $\partial_{k + 1} \circ \partial_{k} = 0$. This can be rewritten as requiring $\im \partial_{k + 1} \subseteq \ker \partial_{k}$. As $\im \partial_{k + 1}$ and $\ker \partial_{k}$ are subspaces of the vector space $X^{(k)}$, we can consider the quotient space $\frac{\ker \partial_{k}}{\im \partial_{k + 1}} \eqqcolon H_{k}$, which is called the $k$\ts{th} homology group. Its dimension as a vector space is an important number, the $k$\ts{th} Betti number $\beta_k \coloneqq \dim(H_k) = \dim(\ker \partial_k) - \dim(\im \partial_{k + 1})$. The alternating sum of these Betti numbers gives the Euler Characteristic 
\begin{equation}
    \chi = \sum_{i = 0}^{k} (-1)^i \beta_i.
\end{equation}

The Betti numbers and Euler characteristic are the main homological quantities we will use to get a quantitive estimate of the ``connectedness" of a simplicial complex $X$. If $X$ has a large $\beta_0$ this tells us there are a lot of disconnected pieces of the complex. A large $\beta_1$ tells us there are a lot of one-dimensional holes in the complex, similar to gluing a bunch of donuts together to tile a big square. Now we explain the simplicial complexes we will construct and the topological data analysis pipeline. The starting point of the TDA pipeline is the data, represented as a collection of points $\mathcal{D} = \set{x_i : 1 \leq i \leq n, x_i \in \mathcal{X}}$, where the only structure we need on the space $\mathcal{X}$ is the ability to compute a distance between points $d(x, y)$. 

Once we have this dataset we then can construct the simplicial complex $X(\epsilon)$ we will compute the homology of. There are two ways to construct this complex, the Vietoris-Rips method and the Cech method. For starters we will stick to the computationally simpler Vietoris-Rips method. The Vietoris-Rips complex $X$ has one node per point $x_i$ in $\mathcal{D}$. From these points we construct a line, or edge, between $(x_i, x_j) \in X^{(1)}$ if $d(x_i, x_j) \leq \epsilon$, where $\epsilon$ is a length scale that filters out far apart nodes. Later we will show how changing $\epsilon$ gives TDA it's power, but for the purposes of illustrating the pipeline we will consider a fixed $\epsilon$ and typically drop the implicit parametrization $X(\epsilon) = X$. Once we have the edges of $X^{(1)}$ we fill in an element $(x_i, x_j, x_k)$ in the next dimension $X^{(2)}$ if and only if these nodes form a clique in $X^{(1)}$, meaning all edges $(x_i, x_j), (x_i, x_k),$ and $(x_j, x_k)$ are present in $X^{(1)}$. We then proceed to higher dimensions, filling in a simplex if there is a clique present in $X^{(1)}$. Clique finding is a notoriously difficult problem without an upper bound on the size of cliques to check, so we put a cap on the dimension $n$, or cliques of size $n + 1$ nodes.

% \begin{figure}
%     \centering
%     \begin{tikzpicture}[main/.style = {draw, rectangle}] 
%             \node[main] (1) at (0, 3) {Weighted graph $G$};
%             \node[main] (2) at (0, 0) {Simplicial Complex $X$};
%             \node[main] (3) at (5.75, 3) {Betti Numbers $\beta_i$};
%             \node[main] (4) at (5.75, 0) {Euler Characteristic $\chi$};
%             \draw [arrow] (1) -- node[left]{Filtration $\epsilon$}(2);
%             \draw [arrow] (2) -- node[left]{$\dim \ker \Delta_i(\epsilon)$} (3);
%             \draw [arrow] (3) -- node[right]{$\sum_i (-1)^i \beta_i(\epsilon)$} (4);
%         \end{tikzpicture}
%     \caption{Basic TDA pipeline}
%     \label{fig:enter-label}
% \end{figure}
\begin{figure}
    \centering
    \begin{tikzpicture}[main/.style = {draw, rectangle}] 
        \node[main] (1) at (0, 0) {Weighted graph \( G \)};
        \node[main] (2) at (4, 0) {Simplicial Complex \( X \)};
        \node[main] (3) at (8, 0) {Betti Numbers \( \beta_i \)};
        \node[main] (4) at (12, 0) {Euler Characteristic \( \chi \)};
        \draw[->, thick, >=latex] (1) -- node[above, yshift=0.5cm]{Filtration \( \epsilon \)} (2);
        \draw[->, thick, >=latex] (2) -- node[above, yshift=0.5cm]{\( \dim \ker \Delta_i(\epsilon) \)} (3);
        \draw[->, thick, >=latex] (3) -- node[above, yshift=0.5cm]{\( \sum_i (-1)^i \beta_i(\epsilon) \)} (4);
    \end{tikzpicture}
    \caption{Basic TDA pipeline}
    \label{fig:enter-label}
\end{figure}



\subsection{Simplicial complexes} \label{sec:simplicial_defs}

We will be working with simplicial complexes and homological constructions, so should give some simple definitions. Let $X^{(0)} = \set{x_1, x_2, \ldots, x_n}$ denote the set of vertices.  
\begin{definition}[Simplicial Complex] \label{def:simplicial_complex}
    A (abstract) simplicial complex defined over a set of points $X^{(0)}$ is a collection $X$ of subsets of $X^{(0)}$ such that if $\tau \in X$ and $\sigma \subseteq \tau$ then $\sigma \in X$. 
\end{definition}

\begin{definition}[n-simplex $\Delta ^ n$] \label{def:n-simplex}
    A geometric figure determined by a collection of $n + 1$ points in Euclidean space $\mathbb{R}^n$. It is defined as a complete graph on $n+1$ vertices or a n-dimensional clique.
\end{definition}

Generally in Homology a n-simplex is formed when $n + 1$ points in Euclidean space $\mathbb{R}^n$ forms a clique, ie when every n-1 simplex contained in the n simplex is formed. However, In this paper \cite{hamilton2023probing} A simplex is formed only when the filtration parameter $\epsilon$ is greater than the functional $F(\rho)$ ie $F(\rho) \leq \epsilon$. We can think of simplex formation as subsets of  $X^{(0)}$ being added to a collections. There are n collections: One collection to contain subsets of size ranging from $1$ to $n$. Sometimes we write n-simplex as $[x_0, .., x_n]$ where $x_i$ are the vertices belonging to the n-simplex

\begin{definition}[Face of simplex] \label{def:n-simplex}
    Given a n-simplex $[x_0, .., x_n]$, we have the simplex containing $n+1$ points. If we delete an arbitrary point from n-simplex then we are left with n points which form a $n$ points which form a $n-1$-simplex following the definition 2 of a simplicial complex. This $n-1$ simplex formed is called the face of the n-simplex
\end{definition}

In \cite{hamilton2023probing}, we are using a functional $F(\rho)$ on subset of vertices and filtration parameter $\epsilon$ such that subset of vertices form a simplex when $F(\rho) \leq \epsilon$. Since every face of a n-simplex is also a simplex we want every face of the n-simplex to form a simplex before the n-simplex is formed. This requires monotonicity from the functional F such that $F(I) \leq F(J) $ for $I \subseteq J$  

\begin{definition}[n-chain] \label{def:n-chain}
    Let $A_1^n, A_2^n, A_3^n, ... A_k^n$ be arbitrary oriented n-simplices of a complex K and an abelian group G, we define an n-chain x with coefficients in G as a formal sum:
    $$x = g_1 \cdot A_1^n + g_2 \cdot A_2^ n + g_3 \cdot A_3^ n + ... g_k \cdot A_k^ n $$
    where $g_i \in G$.
    In most cases $G = Z$. However for our purposes and for the sake of simplicity, we assume $G = \{0, 1\}$ or $Z_2$. Let $L_n$ be the group of n-chains
\end{definition}

\begin{definition}[Boundary of n-simplex] \label{def:Boundary of n-simplex}
    Let $A^n$ be an oriented n-simplex in a complex K. The boundary of $A^n$ is defined as the $n - 1$ chain of K over abelian group G given by 
    $$\delta(A^n) = A_0^{n-1} + A_1^{n-1} + A_2^{n-1} ... + A_n^{n-1}$$
    where $A_i^{n-1}$ is a n-1 face of n-simplex $A^n$. 
    \\ The boundary of $A^n$ is given by n+1 number of $n - 1$ simplex.
\end{definition}
\begin{definition}[Boundary of n-chain] \label{def:Boundary of n-chain}
    For any n-chain, $l = \Sigma_{i=1}^{i=k} g_i \cdot A_i^{n}$ we define the boundary of chain to to be 
    \begin{equation}
        \delta(l) =   \sum_{i=1}^{i=k} g_i \cdot \delta(A_i^{n})
    \end{equation}
    where $A_i^{n}$ are the n-simplexes of K. Therefore, the boundary operator $\delta$ is a homomorphism $\delta$ : $L_n \xrightarrow{} L_{n-1} $
\end{definition}
\begin{definition}[Cycle] \label{def:Cycle}
    When an n-chain has boundary 0, the n-chain is considered a cycle. It is represented as the $Ker(\delta)$
\end{definition}
\begin{definition}[Homology Group $H_n$] \label{def:Homology Group}
    We define the homology Group $H_n = Ker(\delta) / Im(\delta)$
\end{definition}
\begin{definition}[kth Betti Number] \label{def:kth Betti Number}
    We define the kth Betti Number as the rank of the kth homology Group, ie $B_k = rank(H_k)$
\end{definition}
\begin{definition}[Euler Characteristic] \label{def:Euler Characteristic}
    This has two definitions first based on the betti number and another based on the number of simplicial complex. 
    \begin{equation}
        \chi = \sum_i (-1)^i \cdot B_i
    \end{equation}
    Let $n_k$ be the number of k-simplices.
    \begin{equation}
        \chi = \sum_i (-1)^i \cdot n_i
    \end{equation} 
    
\end{definition}

\subsection{Preliminaries}
Assume Graph $G = (V, E)$ to have least 4 vertices and no isolated vertex. Denote $\ket{G}$ as graph state corresponding to graph $G$. For any vertex set $A \subseteq V$, the reduced density matrix $ \rho^A_G $ is defined as:
$
\rho^A_G = \Tr_{V \setminus A} \left( \ket{G} \bra{G} \right)
$. 
The linear entropy (Second Tsallis entropy) of the reduced density operator $\rho^A_G$, represented by $S_2(\rho^A_G) \equiv S_2(A)$, is defined as
\begin{align} \label{eq:linear_entropy}
S_2(A) &= 1 - \Tr\left((\rho^A_G)^2\right) \\
       &= 1 - \sum_{i} \lambda(i)^2  
\end{align}
where \( \lambda(i) \) denotes the \( i \)-th eigenvalue of the reduced density matrix \( \rho^A_G \), with the eigenvalues of \( \rho^A_G \) ordered as \( \lambda_1 \geq \lambda_2 \geq \cdots \geq \lambda_d \).

The 2-deformed correlation function of the reduced density matrix $\rho^A_G $, denoted by $ C_2(\rho^A_G) \equiv C_2(A)$, is computed as:
\begin{equation}
\label{eq:correlation_function}
C_2(A)  = \sum_{v \in A} S_2(v) - S_2(A).    
\end{equation}


\section{Entanglement Distillation} \label{sec:distillable_entanglement}
Quantum gate (or state) teleportation is a foundational protocol in Quantum Computing and information sciences. In Quantum Computing, T-gates are teleported from so called ``magic state" factories to be used to implement T-gates within the operation of an error-correcting code. This is crucial to avoid the Easton-Knill Theorem, which states that the logical operations available to implement transversally (meaning the operation acts on the encoded quantum state) are \emph{not} fully universal and that the two routes to avoid this are to either switch from one quantum code to another, such that all gates can be done, or to create resource states outside of the quantum code and use gate teleportation to apply the gate. Utilizing gate teleportation is a much simpler route that most fault-tolerant research analyzes. Behind this crucial operation of teleportation lies a  primitive known as a Bell pair, which is a pair of entangled qubits in one of the following four states
\begin{equation}
    \frac{\ket{0}\ket{0} \pm \ket{1}\ket{1}}{\sqrt{2}}, \frac{\ket{0}\ket{1} \pm \ket{1}\ket{0}}{\sqrt{2}}. 
\end{equation}
In this section we explore how the number of such pairs that can be extracted, called the Distillable Entanglement, from bipartitions of a multipartite state is related to the Integrated Euler Characteristic (IEC) of an entanglement complex derived from the multipartite state.

Consider a global pure state $\rho = \ketbra{\psi}{\psi}$ over our Hilbert space $\mathcal{H} = (\mathbb{C}^2)^{\otimes n}$ and suppose that we split the state in half, giving a subset $A \subsetneq S$ of qubits to Alice and $B = S \setminus A$ to Bob. Denote their respective states $\rho_A = \Tr_B ( \ketbra{\psi}{\psi})$ and $\rho_B$ similarly. Now imagine the global state happens to be a product state across this bipartition, so $\rho = \rho_A \otimes \rho_B$. No matter what LOCC channels Alice or Bob apply, they will never be able to share a Bell pair between themselves. On the complete opposite end of the spectrum, if the global state is equal to a tensor product of Bell pairs $\rho = \left(\frac{\ket{0}\ket{0} + \ket{1}\ket{1}}{\sqrt{2}} \right)^{\otimes n} \left(\frac{\bra{0}\bra{0} + \bra{1}\bra{1}}{\sqrt{2}} \right)^{\otimes n}$, then we can split up each of the pairs, giving one half to Alice and the other to Bob, and without doing any LOCC they will share $n$ Bell pairs. This number is called the distillable entanglement $E_D$ and it is defined as the upper limit to how many Bell pairs Alice and Bob can create using their part of the state $\rho$, along with LOCC channels. This is defined formally below. 

% \textbf{General Idea}: Does the Integrated Euler characteristic(IEC) tell us anything about the Entanglement distillation \\
% Consider an arbitrary pure state $\ket{\psi}$ lying in Hilbert space $\mathcal{H}$. The corresponding density operator is $\rho = \ket{\psi}\bra{\psi}$.
% We partition the quantum system $\rho$ into two subsystems, A and B, such that their combined state resides in the Hilbert space  $\mathcal{H} = \mathcal{H_A} \otimes \mathcal{H_B}$. The reduced states $\rho_A = \Tr_B(\ket{\psi}\bra{\psi})$ and $\rho_B = \Tr_A(\ket{\psi}\bra{\psi})$ are then sent to Alice and Bob, respectively, each having access only to their state. They are allowed to perform any unitary transformations and measurements, on their respective subsystems and can coordinate their actions through rounds of classical communication (LOCC). Given multiple copies of their respective system, Alice and Bob convert their input to the maximum number of singlets possible.

% The composite quantum state $\rho$, partitioned into subsystems A and B, is represented as $\rho_{AB}$. Given Alice and Bob gets subsystem $\rho_A$ and $\rho_B$ respectively, the maximum number of singlets Alice and Bob can distill using LOCC is represented by $E_D(\rho_{AB})$. In a multi-party scenario, the original state can be partitioned and singlets distilled in several ways by sending observers Alice and Bob different partitions. We introduce the quantity called the average entanglement distillation rate, $\langle E_D \rangle$, which represents the average rate of entanglement distillation across all possible partitions of the multipartite input state. We show that the integrated Euler characteristic can be both upper and lower bounded by the quantity $\langle E_D \rangle$, thereby revealing a connection between Topological Data Analysis and the distillation rate.

\begin{definition} [Distillable Entanglement $E_D(\rho_{AB})$]
Let $\rho = \ketbra{\psi}{\psi}$ be a pure quantum state over a Hilbert space $\mathcal{H}$ with a bipartition $\mathcal{H} = \mathcal{H}_A \otimes \mathcal{H}_B$. Let $\Phi_{A \times B}^{(n)} \in LOCC((\mathcal{H}_A \otimes \mathcal{H}_B)^{\otimes n})$ be a family of ``distilling" channels that utilize only LOCC operations between asymptotically many copies of $\mathcal{H}_A$ and $\mathcal{H}_B$ that aim to create copies of Bell pairs $\tau = \left(\frac{\ket{0}\ket{0} + \ket{1}\ket{1}}{\sqrt{2}} \right) \left(\frac{\bra{0}\bra{0} + \bra{1}\bra{1}}{\sqrt{2}} \right)$. The \emph{distillable entanglement} is then the supremum value of all integers $m$ such that 
$$
\lim_{n \to \infty} F\left( \tau^{\otimes m}, \Phi_{A \times B}^{(n)} (\rho^{\otimes n}) \right) = 1.
$$

% is defined the maximum rate at which singlet states can be distilled from an asymptotically large copies of the arbitrary input quantum state $\rho$ using a Local Operations and Classical Communication (LOCC) protocol.
% \begin{equation} 
%     E_D(\rho) = \sup_{LOCC} \lim_{n \rightarrow \infty} \frac{m}{n}
% \end{equation}
% The LOCC protocol maps n copies of input state $\rho$ to m copies of output singlet states
% \end{definition}
% \begin{definition} [Entanglement Cost $E_C(\rho)$)]
%     Entanglement Cost is defined as the minimum rate at which asymptotic copies of singlet states can be transformed to an arbitrary output state $\rho$ using a Local Operations and Classical Communication (LOCC) protocol.  
% \begin{equation}
%     E_C(\rho) = \inf_{LOCC} \lim_{n \rightarrow \infty} \frac{m}{n}
% \end{equation}
% The LOCC protocol maps n copies of input singlet state to m copies of output state $\rho$
\end{definition}
\begin{definition} [Average Distillable Entanglement]
    Let $\rho = \ketbra{\psi}{\psi}$ be a pure multipartite quantum on Hilbert space $\mathcal{H}_A = \mathcal{H}_{\mathcal{A}_1} \otimes \mathcal{H}_{\mathcal{A}_2} \otimes \dots \otimes \mathcal{H}_{\mathcal{A}_n}$  where $\mathcal{A} := \{\mathcal{A}_1, .... \mathcal{A}_n\}$. The average distillable entanglement is the mean value of the distillable entanglement calculated over all possible bipartitions of $\mathcal{H_A} = \mathcal{H}_J \otimes \mathcal{H}_{J^c}$ where $J \subseteq A$ and $J^c = A \setminus J$
    $$
     \langle E_D \rangle = \frac{\sum_{\substack{J \subseteq \mathcal{A}} }E_D(\rho_{J J^{C}})}{2^n}.
    $$
\end{definition}
\begin{theorem}
Let $\rho = \ketbra{\psi}{\psi}$ be a pure multipartite quantum state on Hilbert space $\mathcal{H}_A = \mathcal{H}_{\mathcal{A}_1} \otimes \mathcal{H}_{\mathcal{A}_2} \otimes \dots \otimes \mathcal{H}_{\mathcal{A}_n}$  where $\mathcal{A} := \{\mathcal{A}_1, \dots \mathcal{A}_n\}$. The reduced Euler characteristic $\tilde{\mathfrak{X}}(\infty)$ of the persistence module created using functional $C(J)_\rho = \sum_{v \in J} S(v)_\rho - S(J)_\rho$ for $J \subseteq A$ is bounded below and above by,

$$ \langle E_D \rangle - \frac{1}{2} \epsilon_{\text{max}}  \leq \frac{\tilde{\mathfrak{X}}(\infty)}{2^n} \leq \langle E_D \rangle$$
where $\langle E_D \rangle$ is the average distillable entanglement of $\rho$ and $\epsilon_{max}$ is that maximum filtration parameter where the barcodes of persistence module stops changes.
\end{theorem}
\begin{proof}
For pure states $\rho_{AB}$, Ref.\cite{bennet_distillation} showed that the entanglement distillation rate, when partitioning the state $\rho$ into subsystems $A$ and $B$, can be quantified by the entropy of entanglement, given by
\begin{equation}
\label{eq:Distillation_Cost_Equality}
     E_D(\rho_{AB}) = S(\rho_A) = -\Tr(\rho_A \log \rho_A)
\end{equation}
where $\rho_A = \Tr_B(\ket{\psi}\bra{\psi})$. For reduced density state $\rho_A$, the von Neumann entropy is denoted as $S(A)_\rho \equiv S(\rho_A)$.
\\
Let $\rho$ be a pure quantum state over Hilbert space $\mathcal{H}_{\mathcal{A}} $. The Hilbert space $ \mathcal{H}_{\mathcal{A}} $ is defined as $ \mathcal{H}_{\mathcal{A}_1} \otimes \mathcal{H}_{\mathcal{A}_2} \otimes \dots \otimes \mathcal{H}_{\mathcal{A}_n} = (\mathbb{C}^2)^{\otimes n} $ where $\mathcal{A} := \{\mathcal{A}_1, .... \mathcal{A}_n\}$. According to Theorem 4.18 in  \cite{hamilton2023probing}, the integrated Euler characteristic is given as a sum over subsets of the total Hilbert space as
% \setlength{\jot}{5pt}
\begin{flalign}
    \tilde{\mathfrak{X}}_q(\infty) &=  \sum_{J \subseteq  \mathcal{A}} (-1)^{|J| - 1} S_q(J)_{\rho}.
\end{flalign}
As $q \rightarrow 1$, Tsallis entropy defined as $S_q(J)_{\rho}$ approaches the von Neumann entropy, $\lim_{q \rightarrow 1} S_q(J)_{\rho} = S(J)_{\rho} = -\Tr(\rho_J \log \rho_J)$. Using von Neumann entropy formalism in previous equation, 
\begin{flalign}
   \tilde{\mathfrak{X}}(\infty) &=  \sum_{J \subseteq  \mathcal{A}} (-1)^{|J| - 1} S(J)_{\rho}  \\
    \label{eq:IEC_rearranged}
    \tilde{\mathfrak{X}}(\infty) &=  \sum_{\substack{J \subseteq \mathcal{A}}}  S(J)_{\rho} - 2 \sum_{\substack{J \subseteq \mathcal{A} \\ |J| \text{mod} 2 = 0}}  S(J)_{\rho} 
\end{flalign}
Dividing equation $\eqref{eq:IEC_rearranged}$ by $2^n$, we get
\begin{flalign}
    \frac{\tilde{\mathfrak{X}}(\infty)}{2^n} &= \frac{\sum_{\substack{J \subseteq \mathcal{A}}}  S(J)_{\rho}}{2^n} - \frac{1}{2^{n-1}}\sum_{\substack{J \subseteq \mathcal{A} \\ |J| \text{mod} 2 = 0}}  S(J)_{\rho} 
\end{flalign}
Substituting in equation \eqref{eq:Distillation_Cost_Equality} in our previous equation, we get
\begin{flalign}
    \frac{\tilde{\mathfrak{X}}(\infty)}{2^n} &= \frac{\sum_{\substack{J \subseteq \mathcal{A}} }E_D(\rho_{J J^{C}})}{2^n} - \frac{1}{2^{n-1}} \sum_{\substack{J \subseteq \mathcal{A} \\ |J| \text{mod} 2 = 0}}  S(J)_{\rho}  
\end{flalign}
where $J^{C} = \mathcal{A} \setminus J$
\begin{flalign}
    \label{eq:IEC_avgDistillation_equality}
    \frac{\tilde{\mathfrak{X}}(\infty)}{2^n} &= \langle E_D \rangle - \frac{1}{2^{n-1}}\sum_{\substack{J \subseteq \mathcal{A} \\ |J| \text{mod} 2 = 0}}  S(J)_{\rho}   \\
     \frac{\tilde{\mathfrak{X}}(\infty)}{2^n} & \leq \langle E_D \rangle
\end{flalign}
as von Neuman Entropy is non-negative, ie $S(J)_\rho \geq 0$ for any $J \subseteq \mathcal{A}$.

The total correlation function for a multipartite quantum state $ \rho $ defined on the set $\mathcal{A} := \{ A_1, .... A_n \}$ is defined as 
\begin{equation}
    C(\mathcal{A})_{\rho} = \sum_{v \in \mathcal{A}} S(v)_{\rho} - S(\mathcal{A})_{\rho} 
\end{equation}
On rewriting the equation, entropy of the system on set $\mathcal{A}$ can be written in terms of the entropy of individual subsystems and correlation function
\begin{equation}
    \label{eq:entropy_in_terms_of_correlation}
    S(\mathcal{A})_{\rho} = \sum_{v \in \mathcal{A}} S(v)_{\rho} -  C(\mathcal{A})_{\rho}
\end{equation}
Substituting in eq \eqref{eq:entropy_in_terms_of_correlation} into eq \eqref{eq:IEC_avgDistillation_equality} yields the following result
\begin{flalign}
    \frac{\tilde{\mathfrak{X}}(\infty)}{2^n} &= \langle E_D \rangle - \frac{1}{2^{n-1}}\sum_{\substack{J \subseteq \mathcal{A} \\ |J|\!\!\!\! \mod 2 = 0}} \left( \sum_{v \in J} S(v)_{\rho} -  C(J)_{\rho} \right) 
\end{flalign}
For an element $v \in A$, the number of even-length subsets that include $v$ can be determined by considering the remaining $n - 1$ elements. Odd-length subsets of the remaining $n-1$ elements are obtained by including v as an element in the set. The number of odd-length subsets of a set with $n-1$ elements is given by: $\sum_{k mod 2 = 1} \binom{n - 1}{k} = 2^{n-2}$.
\begin{flalign}
    \frac{\tilde{\mathfrak{X}}(\infty)}{2^n} &= \langle E_D \rangle - 2^{n-2} \cdot \frac{1}{2^{n-1}}\sum_{v \in \mathcal{A}}  S(v)_{\rho} + \frac{1}{2^{n-1}} \sum_{\substack{J \subseteq \mathcal{A} \\ |J| \!\!\!\!\mod 2 = 0}}  C(J)_{\rho} \nonumber\\
    &=\langle E_D \rangle - \frac{1}{2}\sum_{v \in \mathcal{A}}  S(v)_{\rho} + \frac{1}{2^{n-1}} \sum_{\substack{J \subseteq \mathcal{A} \\ |J| \!\!\!\!\mod 2 = 0}}  C(J)_{\rho}
\end{flalign}
The correlation function is non-negative, a result that follows from the property of subadditivity. By omitting the correlation function from the previous equation, we obtain
\begin{flalign}
    \frac{\tilde{\mathfrak{X}}(\infty)}{2^n} & \geq \langle E_D \rangle - \frac{1}{2} \sum_{v \in \mathcal{A}}  S(v)_{\rho} 
\end{flalign}
Based on the definition provided in \cite{hamilton2023probing},  $\epsilon_{max}$ as the largest value of the filtration parameter at which the number of barcodes changes. For any quantum state $ \rho $ defined on the set $ \mathcal{A} $, $ \epsilon_{\text{max}} = \sum_{v \in \mathcal{A}} S(v)_{\rho} $. At this value of $ \epsilon_{\text{max}} $, the entire topological structure forms a simplex, resulting in the collapse of the barcode into a single 0-dimensional hole. The lower bound can be defined in terms of average entanglement distillation and $\epsilon_{\text{max}}$,
\begin{flalign}
    \frac{\tilde{\mathfrak{X}}(\infty)}{2^n} & \geq \langle E_D \rangle - \frac{1}{2} \epsilon_{\text{max}} 
\end{flalign}
\end{proof}

\section{Graph States} \label{sec:graph_states}


\begin{definition} [Graph State] \label{def:graph_state}

Given a Graph G = (V, E) of finite set $V = \{1 \dots n \}$ and $E \subseteq [V]^2$, graph state $\ket{G}$ corresponding to graph G is a pure quantum state in Hilbert space $(\mathbb{C}^2)^{\otimes n}$ defined by 
\begin{equation}
\label{eq:graph_state}
    \ket{G} = \prod_{(a, b) \in E} U^{\{a,b\}} \ket{+}^{\otimes n}
\end{equation}
where $U^{\{a, b\}}$ is a unitary 2-qubit operation that acts on the qubit corresponding to vertices $a$ and $b$. We assume $U^{\{a, b\}}$ to be the controlled-Z operator, $CZ$, acting on 2 vertices, namely a and b. Each vertex labels a two-level quantum system or qubit.
\end{definition}

\begin{definition} [Stabilizer Operator] \label{def:stabilzer_operator}
    
For a Graph G = (V, E), the stabilizer operator $ K_v $ corresponding to vertex $ v \in V $ is defined as 
\begin{equation}
\label{eq:stabilzer_operator}
    K_v := X_{(v)} \prod_{u \in N(v)} Z_{(u)}
\end{equation}
where $X$ and $Z$ are corresponding Pauli matrices and $N(v)$ is the set of vertices adjacent to vertex $v$ in graph $G$. 
For any vertex $v \in V$, operators $K_v$ commute with other stabilizer operator and are $+1$ eigenstate of $\ket{G}$
\begin{equation}
\label{eq:graph_state_eigenvector_of_stabilzer_operator}
    K_v \ket{G} = \ket{G}
\end{equation}
\end{definition}
\begin{definition} [Stabilizer of Graph State $\ket{G}$] \label{def:stabilizer_of_graph_state}
Given graph G = (V, E) and corresponding graph state $\ket{G}$, the abelian subgroup $S$ of the local pauli-group $\mathcal{P}^{V}$ generated by the set $\{K_v| v \in V\}$ is called the stabilizer of the graph state.
\begin{equation}
\label{eq:stabilizer_of_graph_state}
    \mathcal{S} := \langle K_1, K_2, K_3 \dots K_i \rangle
\end{equation}
where $K_i$ corresponds to the stabilizer operator for the ith vertex
\\
The projector onto the graph state can be represented in terms of the stabilizer operators
\begin{equation}
\label{eq:graph_state_in_terms_of_stabilizer_operators}
    \ket{G}\bra{G} = \frac{1}{2^N} \sum_{\sigma \in \mathcal{S}} \sigma
\end{equation}
    
\end{definition}

\begin{definition} [Stabilizer supported on set $A$] \label{def:stabilizer_support}
Given graph G = (V, E) and let $ A \subseteq V $ be a subset of vertices. We define the set $ \mathcal{S}_A $ as the set of stabilizer operators whose support is restricted to $ A $ as follows:

\begin{equation}
\label{eq:stabilizer_support}
    \mathcal{S_A} := \{ \sigma \in \mathcal{S} | supp(\sigma) \subseteq A \}
\end{equation}
where $ \mathcal{S} $ is the set of all stabilizer operators and $ \text{supp}(\sigma) $ denotes the support of the operator $ \sigma $.

The support of a Pauli operator $ \sigma = \sigma_1 \otimes \cdots \otimes \sigma_n $ is defined as the set of indices $ i \in V $ for which $ \sigma $ acts non-trivially on the corresponding system. Specifically, $ \sigma $ acts non-trivially on vertex $ i $ if and only if the corresponding Pauli operator $ \sigma_i $ is not the identity operator $ \mathbb{I} $. In other words, the support of $ \sigma $, denoted $ \mathcal{S} $, consists of the indices where $ \sigma $ either acts trivially on the systems corresponding to vertices in $ V \setminus A $ or acts non-trivially only on the subset $ A $.
    
\end{definition}

% \begin{align}
%     \mathcal{S} &\coloneqq \\
%     S &\coloneqq
% \end{align}
% \textbf{How do we form barcodes}:  We start with graph G using which we receive our quantum state $\rho_G$. From $\rho_G$ we compute $C_2(\rho_A) = \sum_{v \in A} S_2(v) - S_2(A) $. The 2-deformed correlation function $C_2(\rho_G)$ (also known as linear entropy) is used form simplices such that a subset $A$ forms a simplex when $C_2(\rho_A) \leq \epsilon$ where $\epsilon$ is our filtration parameter. The topological structure formed using this technique is denoted by $\mathcal{X}$. We investigate d-dimensional holes formed by the topological structure $\mathcal{X}$ as we increase the filtration parameter $\epsilon$. There exists an $\epsilon_{max}$ which denotes the $\epsilon$ where the barcodes stops changing. The barcodes formed at various instances of $\epsilon$ is studied.

\begin{prop} \label{prop:calculating_linear_entropy_using_stablizer_support}
    The linear entropy  $S_2(A)_G $ of the reduced density operator $\rho^A_G$ associated with graph $ G = (V, E) $ and vertex set $ A \subseteq V$ can be calculated as:
    \begin{equation} \label{eq:calculating_linear_entropy_using_stablizer_support}
     S_2(A)_G = 1 - \frac{|\mathcal{S}_A|}{2^{|A|}}
    \end{equation}
    where $\mathcal{S}_A$ denotes the set of stabilizer operators for the graph 
$G$ whose support lies on vertices in set $A$.

    
\end{prop}
\begin{proof}
     Let $A \subseteq V$ be a subset of vertices of graph $G$. Let $B$ be the corresponding complement of set A, defined as $B := V\setminus A$. The reduced density operator for set A is denoted by $\rho^A_G := \Tr_B(\ket{G}\bra{G})$. 
     
    Using equation (114) in \cite{hein2006entanglement} we find that,
    \begin{equation}
    \label{eq:partialtrace_stabilizer}
        (\rho^A_G)^2 = \frac{|\mathcal{S}_A|}{2^{|A|}} \rho^A_G
    \end{equation}
    % where 
    % \begin{equation}
    % \label{eq:stabilizer_set}
    %     S_A = \{ \sigma \in S | supp(\sigma) \subseteq A \}
    % \end{equation}
    % The support of Pauli operator $\sigma =  \sigma^1_{i_1} \otimes ... \otimes \sigma^N_{i_N}$ is the set of indices $ a \in V$ for which $\sigma$ acts non-trivially on the system, (ie $i_a \neq 0$ or $\sigma_{i_a} \neq \mathbb{I}$). \\
    Using equation \eqref{eq:partialtrace_stabilizer}, linear entropy $S_2(A)_{G}$ can be calculated as
    \begin{equation}
        S_2(A)_{G} = 1 - \Tr{((\rho^A_G)^2)} = 1 -  \Tr\left( \frac{|\mathcal{S}_A|}{2^{|A|}} \rho^A_G \right) =1 - \frac{|\mathcal{S}_A|}{2^{|A|}}
    \end{equation}
\end{proof}
\begin{prop}
\label{prop:support_stabilizer_subset_of_group_of_stablizer_operator}

For any graph $ G = (V, E) $, let $ A \subseteq V $ be a subset of vertices of size $n$, ie $A = \{1, \dots n\}$. The set of stabilizer operators that are supported on the vertex set $ A $, denoted $ \mathcal{S}_A $, is a subset of the  group of stabilizer operators in set $A$, 
\begin{equation}
\label{eq:support_stabilizer_subset_of_group_of_stablizer_operator}
\mathcal{S}_A \subseteq \langle K_1, K_2, \dots K_n \rangle
\end{equation}

where $K_i$  represents the stabilizer operator associated with vertex $i$ where $i \in A $.

\end{prop}
This proposition is a generalization of what shown in proposition 14 of \cite{hein2006entanglement}
% From the definition of subset
% $$S_A \subseteq \langle K_1, K_2, .. K_i \rangle \iff \forall x : (x \in S_A \implies x \in \langle K_1, K_2, .. K_i \rangle)$$
% Assume there exists $K_i$ where $i \in B$. Let $K_i$ generate a stabilizer operator $K_x$.

% Assume 
% Proving $K_x \not \in S_A$ is sufficient to prove the proposition as the proposition becomes true by contrapositive law. More specifically,
% $$\forall K_x :(K_x \in S_A \implies K_x \in \langle K_1, K_2, .. K_i \rangle) \iff \forall K_x :(K_x \not \in \langle K_1, K_2, .. K_i \rangle \implies K \not \in S_A)$$
% Referring to equation \eqref{eq:stabilzer_operator}, $K_i$ applies $\sigma_x$ on vertex i where $i \in B$. There exists no vertex $j \in V, i \neq j$ such that $K_j$ applies $\sigma_x$ on vertex i. Consequently, $K_x$ will always act non-trivially on vertex $i$, ensuring that $i \in supp(K_x)$. Therefore, $K_x \not \in S_A$ as $supp(\sigma) \not \subset A$. Since we have a contradiction, it must be true that $K$
% $\hfill \blacksquare$

\begin{prop}
\label{prop:entropy_of_single_qubit_in_graph_state}
% Let $ G = (V, E) $ be a graph with vertex set $ V $ and edge set  $E$, and let $ \ket{G} $ denote the corresponding graph state. For any non-isolated vertex $ v \in V $, the reduced density matrix $ \rho^v_G $ is defined as:
% $$
% \rho^v_G = \Tr_{V \setminus \{v\}} \left( \ket{G} \bra{G} \right),
% $$
% where the partial trace is taken over all vertices in $ V $ except $v$. We propose that the second Tsallis entropy  (Linear entropy) of the reduced density matrix $\rho^v_G $, denoted $ S_2(\rho^v_G) $, satisfies:
% For any graph graph G, the linear entropy of the reduced density operator of any non-isolated vertex is $0.5$. 
% non-isolated vertex $v \in V$, the linear entropy of the vertex in graph state $\ket{G}$, denoted as $S(v)_G$, 
% $$
% S_2(\rho^v_G) = 1 - \Tr\left(\rho^v_G{}^2\right)  = 0.5.
% $$
% This suggests that the reduced density matrix for any non-isolated vertex in the graph state has a linear entropy  of $ 0.5 $.
For a graph state \(\ket{G}\) associated with a graph \(G\), the linear entropy \(S_2(\rho^v_G) \equiv S(v)\) of the reduced density matrix for any non-isolated vertex \(v\) is given by:  

\begin{equation}
\label{eq:entropy_of_single_qubit_in_graph_state}
 S(v) = 0.5.
\end{equation}
\end{prop}
% From Proposition 1, We know that $s_A \subseteq \{\mathbb{I}, K_v\}$. From assumption 1, We can conclude stabilizer operator $K_v$ has at least one $\sigma_z$ acting on a vertex u where $u \neq v$. Since $K_v$ acts non trivially on set $V \setminus v$, $K_v \not \in s_A$. Evidently, $I \in s_A$ making $|s_A| = 1$, which gives us $S_2(v) = 0.5$

\begin{proof}
    
    Let \( \mathcal{S}_v \) denote the stabilizer operators supported on vertex \( v \) (see Eq. \eqref{eq:stabilizer_support}). By Proposition \ref{prop:support_stabilizer_subset_of_group_of_stablizer_operator}, \( \mathcal{S}_v \subseteq \{I, K_v\} \), where \( K_v \) is the stabilizer operator for vertex \( v \). Since vertex $v$ is non-isolated, it has at least one neighbor. By definition \ref{def:stabilzer_operator}, the stabilizer operator \( K_v \) applies the \( Z \) operator to the vertices in \( N(v) \). Therefore, $supp(K_v)$ lies outside vertex set $\{v\}$ and $K_v \not \in \mathcal{S}_v$. Evidently, the identity matrix always belongs to $\mathcal{S}_v$ as it acts trivially on all vertices of the graph. The set \(\mathcal{S}_v\) contains only the identity element, so its size is \(|\mathcal{S}_v| = 1\). Substituting this into Equation (\ref{eq:calculating_linear_entropy_using_stablizer_support}), we find \(S_2(\rho^v_G) = 1 - \frac{1}{2} = 0.5\).
\end{proof}

\begin{theorem}
\label{theorem:stabilizer_operator_supported_iff_symmetric_difference}    
    % Let G be a graph, $A \subseteq V$ a set of vertices, and $\mathcal{S}_A$ the set of stabilizers with support contained in $A$. The stabilizer operator $K_{v_1}K_{v_2} \dots K_{v_n} \in \mathcal{S}_A$ where $v_1, v_2, v_3 \dots v_n \in V$ if and only if $(N(v_1) \triangle N(v_2) \triangle \dots \triangle N(v_n)) \subseteq A$.

    Let G be a graph, $A \subseteq V$ a set of vertices, and $\mathcal{S}_A$ the set of stabilizers with support contained in $A$. The stabilizer operator $K = K_{v_1}K_{v_2} \dots K_{v_n}$, for distinct $v_1, v_2, \ldots, v_n \in V$, is contained in $\mathcal{S}_A$ if and only if the disjoint difference of their neighbors is contained in $A$, in symbols $(N(v_1) \triangle N(v_2) \triangle \dots \triangle N(v_n)) \subseteq A$.
\end{theorem}

\begin{proof}
    Let $ v_1, v_2, \dots, v_n $ be a set of vertices in the vertex set $ A $ of the graph $ G $. Let $ N(v_1), N(v_2), \dots, N(v_n) $ denote the sets of neighbors corresponding to each vertex $ v_1, v_2, \dots, v_n $, and define the set $ M = \{ N(v_1), N(v_2), \dots, N(v_n) \} $, which represents the collection of neighborhood sets for the vertices $ v_1, v_2, \dots, v_n $. 

Assume that $K_{v_1}K_{v_2} \dots K_{v_n} \in \mathcal{S}_A$. By proposition \ref{prop:support_stabilizer_subset_of_group_of_stablizer_operator}, vertices $ v_1, v_2, \dots, v_n $ will belong to A. We know that $K_{v_1}K_{v_2} \dots K_{v_n}$ acts trivially on complement of the state $ A $, denoted $ A^c = V \setminus A $ (see Definition \ref{def:stabilizer_support}). It is known that the stabilizer operator $ K_v $ for a vertex $ v \in V $ applies $ X $ operation on the vertex $ v $ and $ Z $ operation on its neighboring vertices. 

% Thus, the operator $ K_{v_1} K_{v_2} \dots K_{v_n} $ acts non-trivially on the complement $ A^c $ by applying $ \sigma_z $ operators to the vertices in $ A^c $. Since $ \sigma_z^2 = I $ (the identity operator), 

It follows that the stabilizer operator $ K_{v_1} K_{v_2} \dots K_{v_n} $ acts trivially on a vertex $ v \in A^c $ if and only if an even number (including zero) of the individual stabilizer operators $ K_{v_1}, K_{v_2}, \dots, K_{v_n} $ applies $Z$ operation on $ v $. This is true because each stabilizer operator can only apply the $Z$ operation on $A^c$ and $ Z^2 = I $.
In terms of the graph $ G $, this means that $ K_{v_1} K_{v_2} \dots K_{v_n} $ acts trivially on a vertex $ v \in A^c $ if an even number of vertices $ v_1, v_2, \dots, v_n $ are adjacent to $ v $. Conversely, if an odd number of vertices $ v_1, v_2, \dots, v_n $ are adjacent to $ v $, then $ K_{v_1} K_{v_2} \dots K_{v_n} $ acts non-trivially, applying a single $ Z $ operator to $ v $.

From the definition of the symmetric difference of neighbor sets, we know:

\begin{equation} 
N(v_1) \triangle N(v_2) \triangle \dots \triangle N(v_n) = \left\{ a \in \bigcup_{v \in \{v_1, v_2, \dots, v_n\}} N(v) : \left| \{ N(v) \in M : a \in N(v) \} \right| \text{ is odd} \right\}.
\end{equation}
This function identifies the vertices of the graph that are adjacent to an odd number of vertices belonging to set \( A \). If a vertex $v$ belongs to $ N(v_1) \triangle N(v_2) \triangle \dots \triangle N(v_n) $ then we know that stabilizer operator $ K_{v_1} K_{v_2} \dots K_{v_n} $ applies a $Z$ operator and acts non-trivially on $v$. Conversely, if a $Z$ operation is being applied to a vertex in graph G then the vertex will belong to $N(v_1) \triangle N(v_2) \triangle \dots \triangle N(v_n)$. Stabilizer operator $ K_{v_1} K_{v_2} \dots K_{v_n} $ can only act on $A^c$ by applying a Z operation. 
% \begin{align}
%     x \in N(v_1) \triangle N(v_2) \triangle \dots \triangle N(v_n) \iff 
% \end{align}

% Recall that $ v \in \text{supp}( K_{v_1} K_{v_2} \dots K_{v_n}) $ if $ K_{v_1} K_{v_2} \dots K_{v_n} $ acts non-trivially on vertex $ v $.

We conclude that for a vertex $ v \in A^c $, $ v \in \text{supp}( K_{v_1} K_{v_2} \dots K_{v_n}) $ if and only if $ v \in N(v_1) \triangle N(v_2) \triangle \dots \triangle N(v_n)$. Therefore, $ K_{v_1} K_{v_2} \dots K_{v_n} \in \mathcal{S_A} $ if and only if for all $ v \in A^c $, $ v \notin N(v_1) \triangle N(v_2) \triangle \dots \triangle N(v_n) $. 

In other words, we have:

\begin{equation}
K_{v_1} K_{v_2} \dots K_{v_n} \in \mathcal{S_A} \iff N(v_1) \triangle N(v_2) \triangle \dots \triangle N(v_n) \subseteq A.
\end{equation}

\end{proof}


% Since $\{v_1, v_2, v_3 \dots v_n\} \subseteq A$, $K_{v_1}K_{v_2} \dots K_{v_n}$ can only apply a $\sigma_z$ operation on vertices outside A.


% If even number of stabilizer operator applies $\sigma_z$ operation on vertex $w \in V \setminus A$ then it leads a vanishing Pauli matrix ie $\sigma_z^m = \identity$ where m is an even integer. 


% From the definition of $S_A$ we know that  $K_{v_1}K_{v_2} \dots K_{v_n} \in S_A$ if and only if $K_{v_1}K_{v_2} \dots K_{v_n}$ acts trivially on $V \setminus A$.

% Stabilizer operator $K_v$ applies $\sigma_x$ operation on vertex v and $\sigma_z$ operation on its neighboring vertices, ie $K_v = \sigma_x^{v}\sigma_z^{N(v)}$. Let $v \in V$. Vertex v has the $\sigma_z$ operator acting on it when odd number of operators in $K_{v_1}K_{v_2} \dots K_{v_n}$ applies the $\sigma_z$ on vertex v. If even 


% Any stabilizer operator $K_v$ can only act non-trivially outside set A by apply $\sigma_z$ operator on $N(v) \setminus A$. If even number of stabilizer operator is applying the $\sigma_z$ operator on any vertex $w \in V \setminus A$ then the Pauli operator vanishes, ie $\sigma_z^m = \identity$ if m is even. 
 
%  Therefore, $K_{v_1}K_{v_2} \dots K_{v_n}$ can act trivially on $w \in V \setminus A$ only if even number of stabilizer operators in $K_{v_1}, K_{v_2} \dots K_{v_n}$ has neighbor w. $K_{v_1}K_{v_2} \dots K_{v_n}$ acts non-trivially on $w \in V \setminus A$ if odd number of stabilizer operators applies the $\sigma_z$ operation on vertex $v \in A \setminus V$.
 
%  We consider the symmetric difference of the neighboring set  $v_1, v_2, v_3 \dots v_n$ denoted by

 
 
%  Each stabilizer operator $K_v$ applies $\sigma_z$ operation on vertices $N(v)$ which may lie out side set $A$. The operations of $K_v$ has operations outside set $A$ if it has neighbors outside set $A$ i which case it applies $\sigma_z$ operations. Any vertex $v \in \{v_1, v_2, v_3 \dots v_n\}$, acts non-trivially on set $V\setminus A$ by applying $\sigma_z$ operation on vertices of $N(v) \setminus A$. This $sigma_z$ operation vanishes if another $K_w$ applies a $\sigma_z$ operation on the same vertex. Since $\sigma_z^m = \identity$ if m is even, 



% From 

% From the definition of sup


\begin{prop}
\label{prop:conditions_for_belonging_to_support_stabilizer}
% Let $G = (V, E)$ be a graph with vertex set V. For every vertex pair $u, v \in V$,  $(N(u) \setminus v) = \emptyset$ if and only if  $K_u \otimes \mathbb{I} \in S_{u,v}$ where $K_u$ is the stabilizer operator associated with vertex u and $S_{u, v}$ is the set of stabilizer operator for graph state $\ket{G}$ contained in subset $\{u, v\}$

Assume a graph $G = (V, E)$ with no isolated vertices, let $(u, v)$ be a pair of vertices in $V$. We propose
% The stabilizer operator $K_u \otimes \mathbb{I}$ has support on the vertex pair $(u, v)$ if and only if $u$ is a leaf vertex with parent $v$

\begin{enumerate}
    \item $ K_u \in \mathcal{S}_{u,v} $ if and only if $ (N(u) \setminus \{v\}) = \emptyset $.
    \item $ K_v \in \mathcal{S}_{u,v} $ if and only if $ (N(v) \setminus \{u\}) = \emptyset $.
    \item $ K_u K_v \in \mathcal{S}_{u,v} $ if and only if $ (N(u) \setminus \{v\}) = (N(v) \setminus \{u\}) $.
\end{enumerate}
 where $K_u$ and $K_v$ are the stabilizer operator corresponding to vertex $u$ and $v$ respectively, and $\mathcal{S}_{u,v}$ is the set of stabilizer operators whose support lies in the vertex set $\{u, v\}$. 

\end{prop}
% If $(N_u = \{ v \}$ and $|N_v| > 1)$  then evidently, $K_u \otimes \mathbb{I} \in s_{u,v}$ as support of $K_u \otimes \mathbb{I}$ is a subset of $\{u, v \}$.

\begin{proof}
By Theorem \ref{theorem:stabilizer_operator_supported_iff_symmetric_difference}, $ K_u \in \mathcal{S}_{u,v} \iff N(u) \subseteq \{u, v\} $. Given that vertex $ u $ is non-isolated, we know that the neighborhood $ N(u) $ contains at least one element. Assuming $ N(u) \subseteq \{u, v\} $ and $ |N(u)| > 1 $, it follows that $ N(u) = \{v\} \textit{ or }  (N(u) \setminus \{v\}) = \emptyset$. The reverse direction follows trivially: if $(N(u) \setminus \{v\}) = \emptyset$ or equivalently $ N(u) \subseteq \{v\} $, then the stabilizer operator (See definition \ref{def:stabilzer_operator}) corresponding to vertex $u$ only acts on vertex set $\{u, v\}$ (using assumption vertex $u$ is non-isolated). Therefore, $supp(K_u) \subseteq \{u, v\}$ and $K_u \in S_{u,v}$. Similar argument follows for $ K_v \in S_{u,v} \iff (N(v) \setminus \{u\}) = \emptyset $.

 
 % Additionally, given the assumption that $ G $ contains no self-loops, we have $u \not \in N(u)$. We can can conclude that $ N(u) \subseteq \{u, v\} $ if and only if vertex $ u $ is a leaf vertex connected to vertex $ v $, ie $N(u) = {\v\}$ or $(N(u) \setminus \{v\}) = \emptyset.$ Similar argument follows for $ K_v \in S_{u,v} $.

From Theorem \ref{theorem:stabilizer_operator_supported_iff_symmetric_difference}, it follows that $K_u K_v \in S_{u,v} \iff N(u) \triangle N(v) \subseteq \{u, v\}$ or equivalently $(N(u) \setminus N(v)) \cup (N(v) \setminus N(u)) \subseteq \{u, v\}$. Since the graph $G$ is simple, $(N(u) \setminus N(v)) \subseteq \{v\}$ and $(N(v) \setminus N(u)) \subseteq \{u\}$. This means that either $N(u) = \{v\} \cup (N(u) \cap N(v))$ or $N(u) = N(u) \cap N(v)$. Similarly, $N(v) = \{u\} \cup (N(v) \cap N(u))$ or $N(u) = N(v) \cap N(u)$. On subtracting the respective vertices we get the expression, $N(u) \setminus \{v\}= N(u) \cap N(v)$ and $N(v) \setminus \{u\}= N(u) \cap N(v)$. Therefore, we conclude that the expression $N(u) \triangle N(v) \subseteq \{u, v\}$ is equivalent to the expression  $ (N(u) \setminus \{v\}) = (N(v) \setminus \{u\}) $. Thus we conclude that $ K_u K_v \in S_{u,v} $ if and only if $ (N(u) \setminus \{v\}) = (N(v) \setminus \{u\}) $.



% Since G contains no self-loops, $N(u) \setminus N(v) = \emptyset$ or $N(u) \setminus N(v) = \{v\}$. Similarly, $N(v) \setminus N(u) = \emptyset$ or $N(v) \setminus N(u) = \{u\}$. We can conclude $(N(u) \setminus \{v\}) = (N(v) \setminus \{u\})$ as set $N(u)$ can differ from set $N(v)$ solely by elements $u$ or $v$.
    % Let $u, v \in V$ be a vertex pair and assume that $N(u)\setminus v = \emptyset$. This means that vertex $ u $ has exactly one neighbor, which is vertex $ v $. According to the definition of stabilizer operators, the stabilizer operator $ K_u $ applies the $ \sigma_x $ operator to vertex $ u $ and the $ \sigma_z $ operator to vertex $ v $. Since the identity operator acts trivially on all vertices, the stabilizer operator $K_u \otimes \mathbb{I}$ only acts non-trivially on vertex set $\{u, v\}$, $supp(K_u \otimes \mathbb{I})\setminus \{u,v\} = \emptyset$. Therefore, $K_u \otimes \mathbb{I} \in S_{u,v}$.

    % Let $u, v \in V$ be a vertex pair and assume that $K_u \otimes \mathbb{I} \in S_{u,v}$. Assuming that graph $ G $ has no isolated vertices, it follows that vertex $ u $ has at least one neighbor, denoted as $ w $. Assume, for the sake of contradiction, that $ w \notin \{u, v\} $. Under this assumption, the stabilizer operator $ K_u $ applies the $ \sigma_z $ operator to vertex $ w $, which implies that $ w $ is included in the support of $ K_u $. This would contradict our assumption of $K_u \otimes \mathbb{I} \in S_{u,v}$ as $ w \in \text{supp}(K_u \otimes \mathbb{I}) \setminus \{u, v\} $ is non-empty. Since G is a simple graph, the neighbor of u must be the vertex v in which case the operator $K_u$ will apply $\sigma_z$ on vertex v and have its support contains within set $\{u, v\}$. We can conclude that $(N(u) \setminus \{v\}) = \emptyset$
\end{proof}

% \begin{prop}
% % Let $G = (V, E)$ be a graph with vertex set V. For every vertex pair $u, v \in V$, $(N(u)\setminus v) = (N(v)\setminus u )$ if and only if  $K_u \otimes K_v \in S_{u,v}$ where $K_u$ is the stabilizer operator associated with vertex u and $S_{u, v}$ is the set of stabilizer operator for graph state $\ket{G}$ contained in subset $\{u, v\}$

% Assume graph $G = (V, E)$ has no isolated vertices and let $(u, v)$ be a pair of vertices in $V$. The stabilizer operator $K_u K_v$ has support on the vertex pair $(u, v)$ if and only if vertex and $u$ and $v$ share the same neighbors (excluding $u$ and $v$ themselves)

% $$
% K_u K_v \in S_{u,v} \iff (N(u)\setminus v) = (N(v)\setminus u ) 
% $$
%  where $K_u, K_v$ are the stabilizer operator corresponding to vertex $u$ and $v$ respectively, and $S_{u,v}$ is the set of stabilizer operators whose support lies in the vertex set $\{u, v\}$.
% \end{prop}

% From theorem ??, $K_u K_v \in S_{u,v}$ iff $N(u) \triangle N(v) \subseteq \{u, v\}$. From the definition of symmetric sets, 

% Let $ u, v \in V $ be a pair of vertices, and assume that $ K_u K_v \in S_{u,v} $.From the definition of $S_{u, v}$ in \eqref{eq:stabilizer_set} we know that $ K_u K_v \in S_{u,v} $ if and only if $ K_u K_v $ acts trivially on $ V \setminus \{u, v\} $. The stabilizer operator $ K_u $ applies the $ \sigma_x $ operator to vertex $ u $ and the $ \sigma_z $ operator to the vertices in the neighborhood $ N(u) $. Similarly, the stabilizer operator $ K_v $ applies $ \sigma_x $ to vertex $ v $ and $ \sigma_z $ to the vertices in $ N(v) $.

% Therefore, $ K_u K_v $ acts trivially on the vertex set $ V \setminus \{u, v\} $ if and only if $ N(u) \setminus \{u, v\} = N(v) \setminus \{u, v\} $; the neighborhoods of vertices $ u $ and $ v $ outside of $ \{u, v\} $ must be identical in which case the both the vertices applying $\sigma_z$ on $ V \setminus \{u, v\} $ will lead to the identity operator. Since we are dealing with simple graphs, it follows that $ u \notin N(u) $ and $ v \notin N(v) $. This implies that:

% $$
% N(u) \setminus \{u, v\} = N(u) \setminus \{v\} \quad \text{and} \quad N(v) \setminus \{u, v\} = N(v) \setminus \{u\}.
% $$

% Finally giving us that $K_u K_v \in S_{u,v} \iff (N(u)\setminus v) = (N(v)\setminus u )$



% The stabilizer operator $ K_u $ applies the $ \sigma_z $ operator to the vertices in the neighborhood $ N(u) $, while the stabilizer operator $ K_v $ applies the $ \sigma_z $ operator to the vertices in the neighborhood $ N(v) $. Given our assumption that $ N(u) \setminus \{v\} = N(v) \setminus \{u\} $, both stabilizer operators $ K_u $ and $ K_v $ apply the $ \sigma_z $ operator to the vertices in set $ N(v) \setminus \{u, v\} =  N(u) \setminus \{u, v\}$. Since $ \sigma_z^2 = \identity $, the operator $ K_u \otimes K_v $ acts trivially on the set $ V \setminus \{u, v\} $. Therefore, the support of the operator $ K_u \otimes K_v $ is contained within the set $ \{u, v\} $. As a result, we conclude that $ K_u \otimes K_v \in S_{u,v} $.

% For any vertex pair $u, v \in V$, assume $K_u \otimes K_v \in S_{u,v}$, implying $supp(K_u \otimes K_v) \setminus \{u, v\} = \emptyset$ or $supp(K_u \otimes K_v) \subseteq \{u, v\}$. Lets assume a contradiction that $(N(u)\setminus v) \neq (N(v)\setminus u)$.WLOG, there exist $w \in V \setminus \{u, v\}$ such that w is exists in $(N(u)\setminus v)$ and not in $(N(v)\setminus u)$. This implies that $w \in supp(K_u \otimes K_v)$ as $K_u$ applies $\sigma_z$ and $K_v$ applies identity to vertex w. However, this violates our assumption that $supp(K_u \otimes K_v) \setminus \{u, v\} $. Therefore, $(N(u)\setminus v) = (N(v)\setminus u)$. 

% \begin{prop}
%     Given graph G = (V, E) and corresposnding graph state $\ket{G}$.
%      For any non-isolated pair of vertices $ u,v \in V $, the reduced density matrix $ \rho^{u,v}_G $ is defined as:
% $$
% \rho^{u,v}_G = \Tr_{V \setminus \{u, v\}} \left( \ket{G} \bra{G} \right),
% $$
% where the partial trace is taken over all vertices in $ V $ except $u, v$.


% Given a graph $ G = (V, E) $, we propose that the 2-deformed correlation function for any vertex pair $ (u, v) $, denoted $ C_2(u, v) $, satisfies the following condition:

% $$
% C_2(u, v) = 0.25 \iff (N(u) \setminus \{v\}) \neq (N(v) \setminus \{u\}) \land (N(u) \setminus \{v\}), (N(v) \setminus \{u\}) \neq \emptyset
% $$

% where $ N(u) $ and $ N(v) $ represent the neighborhoods of vertices $ u $ and $ v $, respectively.
% \end{prop}

% This results follows from proposition 14 shown in \cite{hein2006entanglement} that stabilizer group with support on $\{u, v\}$ has only one element,  the identity operator, ie $|S_{u, v}| = 1$. Using this result in eq \eqref{eq:partialtrace_stabilizer}, we get that $C_2(u, v) = 0.25$.

\begin{prop} \label{prop:correlation_function_relation_with_graph_structure}
Given a graph $ G = (V, E) $ with no isolated vertices, we propose that the 2-deformed correlation function for any vertex pair $ (u, v) $, denoted $ C_2(u, v) $, satisfies the following conditions:
\begin{enumerate}
    \item $C_2(u, v) = 1 \iff (N(u) \setminus \{v\} = N(v) \setminus \{u\} = \emptyset)$
    \item
    $C_2(u, v) = 0.5 \iff 
\begin{aligned}(N(u) \setminus \{v\} = N(v) \setminus \{u\} \neq \emptyset) \text{ or } \\
(N(u) \setminus \{v\} = \emptyset \text{ and } N(v) \setminus \{u\} \neq \emptyset) 
\text{ or } \\
(N(v) \setminus \{u\} = \emptyset \text{ and } N(u) \setminus \{v\} \neq \emptyset)
\end{aligned}$

% \begin{align}
%     lS
% \end{align}

% $C_2(u, v) = 0.5  \iff (N(u) \setminus \{v\} = N(v) \setminus \{u\} \neq \emptyset) \text{ or } (N(u) \setminus \{v\} = \emptyset \text{ and } N(v) \setminus \{u\} \neq \emptyset) \text{ or }  (N(v) \setminus \{u\} = \emptyset \text{ and } N(u) \setminus \{v\} \neq \emptyset)$
    \item $ C_2(u, v) = 0.25 \iff (N(u) \setminus \{v\}) \neq (N(v) \setminus \{u\}) \text{ and } (N(u) \setminus \{v\}), (N(v) \setminus \{u\}) \neq \emptyset $

\end{enumerate}

where $ N(u) $ and $ N(v) $ represent the neighborhoods of vertices $ u $ and $ v $, respectively.
\end{prop}
Assume a pair of vertices $u, v \in V$. From proposition \ref{prop:entropy_of_single_qubit_in_graph_state}, we get the the linear entropy of vertices $u$ and $v$ is $0.5$. Plugging in these values in equation for 2-deformed correlation function, 

\begin{align}
    C_2(u, v) &= S_2(u) + S_2(v) - S_2(u, v) \\
    &=0.5 * 2 - \left(1 - \frac{|\mathcal{S}_{u,v}|}{2^{|\{u,v\}|}}\right) \\
\label{eq:correlation_function_relation_to_number_of_stabilizer_operator}
    &= \frac{|\mathcal{S}_{u,v}|}{4} 
\end{align}
\begin{itemize}
    \item \textbf{Condition 1}: We start with the above equation that establishes the condition $ C_2(u, v) = 1 \iff |\mathcal{S}_{u,v}| = 4 $. This condition is satisfied if and only if $ \mathcal{S}_{u,v} = \{\identity, K_u, K_v, K_uK_v\} $ as $\mathcal{S}_{u,v} \subseteq \langle K_u, K_v \rangle$ (see proposition \ref{prop:support_stabilizer_subset_of_group_of_stablizer_operator}). According to proposition 
    \ref{prop:conditions_for_belonging_to_support_stabilizer}, the set $ \mathcal{S}_{u,v} $ can be expressed as $ \{\identity, K_u, K_v, K_uK_v\} $ if and only if both $ N(u) \setminus \{v\} = \emptyset $ and $ N(v) \setminus \{u\} = \emptyset $. These conditions imply that $ N(u) \setminus \{v\} = N(v) \setminus \{u\} = \emptyset $. Consequently, we arrive at the condition that:

    \begin{equation}
    C_2(u, v) = 1 \iff (N(u) \setminus \{v\} = N(v) \setminus \{u\} = \emptyset).
    \end{equation}
    
    \item \textbf{Condition 2}: From equation \ref{eq:correlation_function_relation_to_number_of_stabilizer_operator} we get the equality that  $ C_2(u, v) = 0.5 \iff |\mathcal{S}_{u,v}| = 2 $. Since the identity operator is trivially always part of $\mathcal{S}_{u,v}$. The condition $|\mathcal{S}_{u,v}| = 2 $ is true if and only if only one of $K_u$ or $K_v$ or $K_{u, v}$ is part of $\mathcal{S}_{u,v}$. This enforces the constraint that the conditions presented in proposition \ref{prop:conditions_for_belonging_to_support_stabilizer} are exclusive. In other words, if one of the conditions are true then the rest of the conditions becomes false. 
    Lets look at the case when $K_u \in \mathcal{S}_{u,v}$ while $K_v \not \in \mathcal{S}_{u, v} \text{ and } K_{u, v} \not \in \mathcal{S}_{u, v}$. Using \ref{prop:conditions_for_belonging_to_support_stabilizer}, we get the condition that $(N(u) \setminus \{v\}) = \emptyset $ and $(N(v) \setminus \{u\}) \neq \emptyset $. Similar results is obtained when considering $K_v \in \mathcal{S}_{u,v}$ while $K_u \not \in \mathcal{S}_{u, v} \text{ and } K_{u, v} \not \in \mathcal{S}_{u, v}$. 
    Assume $K_uK_v \in \mathcal{S}_{u,v}$ and $K_u \not \in S_{u, v} \text{ and } K_v \not \in \mathcal{S}_{u, v}$. Using \ref{prop:conditions_for_belonging_to_support_stabilizer}, we get the conditions that $ (N(u) \setminus \{v\}) = (N(v) \setminus \{u\}) $ and $(N(u) \setminus \{v\}) \neq \emptyset$ and $(N(v) \setminus \{u\}) \neq \emptyset$. Summarizing the results we get that 
    
    $$C_2(u, v) = 0.5 \iff 
\begin{aligned}(N(u) \setminus \{v\} = N(v) \setminus \{u\} \neq \emptyset) \text{ or } \\
(N(u) \setminus \{v\} = \emptyset \text{ and } N(v) \setminus \{u\} \neq \emptyset) 
\text{ or } \\
(N(v) \setminus \{u\} = \emptyset \text{ and } N(u) \setminus \{v\} \neq \emptyset)
\end{aligned}$$

    
    \item \textbf{Condition 3}: From equation \ref{eq:correlation_function_relation_to_number_of_stabilizer_operator}, we can form condition that $C_2(u, v) = 0.25 \iff |\mathcal{S}_{u,v}| = 1$. This follows from the result presented in \cite{guhne2009entanglement}, which states that all stabilizer operators $\sigma$ of graph $ G $ (except for the identity operator) have support on vertices other than $ u $ and $ v $ ($\sigma \not \in \mathcal{S}_{u, v}$) if and only if $ (N(u) \setminus \{v\}) \neq (N(v) \setminus \{u\}) $ and both $ (N(u) \setminus \{v\}) $ and $ (N(v) \setminus \{u\}) $ are non-empty. Thus we arrive that the conclusion that 
    \begin{equation}
        C_2(u, v) = 0.25 \iff (N(u) \setminus \{v\}) \neq (N(v) \setminus \{u\}) \text{ and } (N(u) \setminus \{v\}), (N(v) \setminus \{u\}) \neq \emptyset
    \end{equation} 
\end{itemize}


% such that $(N(u) \setminus v), (N(v) \setminus u) = \emptyset$. The support of stabilizer operator $K_u$ is the set $\{u, v\}$ because $K_u$ applies $\sigma_x$ on vertex $u$ and $\sigma_z$ on vertex $v$. Similarly, the support of $K_v$ is $\{u, v\}$. Therefore the support of group $\langle K_u, K_v \rangle \subseteq \{a, b\}$. Denote $S_{u, v}$ the set of stabilizer operators which have support on set $\{a, b\}$. $ S_{u, v} = \langle K_u, K_v \rangle$ as argument above and proposition 1. The size of $S_{u, v}$ is 4. Plugging in the values in equation\eqref{eq:Entropy_from_stabilizer},
% \begin{align}
%     C_2(\rho^{u, v}_G) &= S_2(u)_G + S_2(v)_G - S_2(u, v)_G \\
%     &=0.5 * 2 - \left(1 - \frac{|S_A|}{2^{|A|}}\right) \\
%     &= 1,
% \end{align}
% where we used Proposition 3 and Proposition 1 to compute $S_2$ for $u$ and $v$ and 
% $$C_2(\rho^{u, v}_G) = 1$$ as $|S_A| = 4$ and $2^{|A|} = 4$

% Assume for vertices $u, v \in V$, $C_2(\rho^{u, v}_G)$. Using equation \eqref{eq:Entropy_from_stabilizer} and proposition 3, 
% $$C_2(\rho^{u, v}_G) = S_2(u)_G + S_2(v)_G - S_2(u, v)_G$$
% $$1 = 0.5 * 2 - 1 + \frac{|S_A|}{2^{2}}$$
% $$|S_A| = 4$$
% This implies that $S_A  = \{\mathbb{I}, K_u \otimes \mathbb{I}, \mathbb{I} \otimes K_v, K_u \otimes K_v \}$. Using proposition 4, we conclude that $N(u) \setminus v = \emptyset$ and $N(v) \setminus u = \emptyset$. We have shown $N(u) \setminus v = N(v) \setminus u = \emptyset$. 

% \begin{prop}
% Given a graph $ G = (V, E) $, we propose that the 2-deformed correlation function for any vertex pair $ (u, v) $, denoted $ C_2(u, v) $, satisfies the following condition:

% \begin{align*}
% C_2(u, v) = 0.5 & \iff (N(u) \setminus \{v\} = N(v) \setminus \{u\} \neq \emptyset) \\
% & \lor (N(u) \setminus \{v\} = \emptyset \land N(v) \setminus \{u\} \neq \emptyset) \\
% & \lor (N(v) \setminus \{u\} = \emptyset \land N(u) \setminus \{v\} \neq \emptyset)
% \end{align*}

% where $ N(u) $ and $ N(v) $ represent the neighborhoods of vertices $ u $ and $ v $, respectively.
% \end{prop}

% From Proposition 1 we know that $S_A \subseteq \{ \mathbb{I}, K_u \otimes \mathbb{I}, \mathbb{I} \otimes K_v, K_u \otimes K_v \} $. If $C_2(u, v) = 0.5$ then $|s_A| = 2$. Since $\mathbb{I} \in S_A$, we find that $K_u \otimes \mathbb{I} \in s_{u,v}$ OR $ \mathbb{I} \otimes K_v \in s_{u, v}$ OR $K_u \otimes K_v \in s_{u, v}$. 
% For any vertex pair $u, v \in V$, assume that $C_2(u, v) = S_2(u) + S_2(v) - S_2(u, v) = 0.5$. Using proposition 3 and equation(\ref{eq:Entropy_from_stabilizer}), we can conclude that $|S_{u,v}| = 2$.  From Proposition 1, $S_{u,v} \subseteq \{ \mathbb{I}, K_u \otimes \mathbb{I}, \mathbb{I} \otimes K_v, K_u \otimes K_v \} $. Trivially, $\mathbb{I} \in S_{u,v} $. Therefore, 



\begin{prop}
\label{prop:complete_graph_iff_neighbor_set_condition}
   For a graph G with no isolated vertices, Graph $G = (V, E)$ is a complete graph if and only if $N(u) \setminus \{v\} = N(v)\setminus \{u\}$ for every $u,v \in V$.
\end{prop}
\begin{proof} 
Consider graph $G = (V, E)$ to be a complete graph, we will show that $N(u) \setminus \{v\} = N(v)\setminus \{u\}$ for every $u,v \in V$. Let $u, v$ be vertices in $G$, $u, v \in V$. By definition of complete graph, every vertex pair in graph $G$ is connected by an unique edge. The neighborhood of $u$ and $v$ is $N(u) = V \setminus \{u\}$ and $N(v) = V \setminus \{v\}$ respectively. Computing $N(u) \setminus v$ and $N(v) \setminus u$ yields, 
\begin{equation}
N_u \setminus \{v\} = N_v \setminus \{u\} = V \setminus \{u, v\}    
\end{equation}
Hence, if the graph G is a complete graph, then $N(u) \setminus v = N(v)\setminus u$ for every $u,v \in V$.

Consider a graph $ G = (V, E) $ with no isolated vertex. Assume that $ N(u) \setminus \{v\} = N(v) \setminus \{u\} $ for any distinct vertex pair $ u, v \in V $. We will show that G is complete. To reach a contradiction, assume that $G$ is not complete. Consequently, let $ u $ and $ v $ be two non-adjacent vertices in $ G $. Since $ G $ has no isolated vertices, vertices $u$ and $v$ must have at least 1 neighbor. Let vertex $x$ be adjacent to vertex $u$ and vertex $y$ be adjacent to vertex $v$. Since $ N(x) \setminus \{y\} = N(y) \setminus \{x\} $ and $v \in N(y) \setminus \{x\}$, it follows that vertex $ x $ is adjacent to vertex $ v $; $v \in N(x) \setminus \{y\}$. Applying this reasoning again to vertices $ x $ and $ v $, we find that $N(x) \setminus \{v\} = N(v) \setminus \{x\}.$ Since $ u \in N(x) \setminus \{v\} $, we conclude that vertex $ v $ must also be adjacent to vertex $ u $. This leads to a contradiction with our assumption that $ u $ and $ v $ are non-adjacent vertices and concludes any two vertices in $G$ must be adjacent. Therefore $G$ is complete.
\end{proof}

\begin{lemma} \label{lemma:correlation_function_value_relation_with_topological_graph}
 
Given a graph $ G $ and its corresponding graph state $ \ket{G} $, the topological structure $ \mathcal{X} $ associated with $ \ket{G} $ is such that for $ 0 \leq \epsilon < 0.5 $, the structure consists of disconnected vertices. At $ \epsilon = 0.5 $, the structure forms a complete graph if and only if for every pair of vertices $ (u, v) $ in $ G $, the correlation function satisfies $ C_2(u, v) = 0.5 $.
\end{lemma}

\begin{proof}
The topological structure $ \mathcal{X} $ associated with the graph state $ \ket{G} $ is defined in terms of a deformed correlation function, as given in equation \eqref{eq:correlation_function}. Specifically, for any subset of qubits $ A \subseteq V $ in the graph state $ \ket{G} $, the vertices corresponding to $ A $ form a simplex in $ \mathcal{X} $ when the filtration parameter $ \epsilon $ exceeds or equals the value $ C_2(A) $, i.e. $ \epsilon \geq C_2(A) $. The vertices in topological structure $ \mathcal{X} $ remains disconnected in the interval $ [0, 0.5) $ if and only if $ C_2(u, v) < 0.5 $ for each pair of qubits $ u, v \in V $. In other words, for the graph state $ \ket{G} $, the vertices corresponding to pairs of qubits $ u $ and $ v $ do not form an edge and consequently the number of connected component remains unchanged.
Furthermore, $ \mathcal{X} $ becomes a complete graph at $ \epsilon = 0.5 $ if and only if every possible 1-simplex is present at $ \epsilon = 0.5 $, which occurs precisely when $ C_2(u, v) = 0.5 $ for all pairs of qubits $ u, v \in V $. 
    % associated with graph $ G $. An edge between the vertices in $ \mathcal{X} $ representing qubits $ u $ and $ v $ is created when the filtration parameter $ \epsilon $ exceeds or is equal to $ C_2(u, v) $. This follows because the topological structure remains disconnected in the interval $ [0, 0.5) $ if $ C_2(u, v) < 0.5 $ for each pair of qubits, and forms a complete graph when $ C_2(u, v) = 0.5 $, as every edge is formed when the filtration parameter exceeds 0.5.
\end{proof}

% By the assumption that $ N(u) \setminus \{v\} = N(v) \setminus \{u\} $, there must exist a vertex $ w \in V $ such that $ w $ is adjacent to both $u$ and $v$. From the same assumption, $ N(w) \setminus \{u\} = N(u) \setminus \{w\} $. Since $ v \in N(w) \setminus \{u\} $ but $ v \notin N(u) \setminus \{w\} $, this creates a contradiction.

% Therefore, the initial assumption that $G$ is not complete must be false. Hence, if for a connected graph $G$, $ N_G(u) \setminus \{v\} = N_G(v) \setminus \{u\} $ for every pair $u, v \in V $, then $G$ must be a complete graph.

\begin{theorem}
Graph G is a complete graph or star graph if and only if its corresponding topological structure $\mathcal{X}$ has n disconnected vertices between  $ 0 \leq \epsilon < 0.5 $ and forms a complete graph at  $ \epsilon = 0.5 $. We assume $\mathcal{X}$ to represent the topological structure of a Graph state with no isolated vertices.
\end{theorem}
\begin{proof}
    \textbf{Proof in forward direction:} Assume $ G $ is an $ n $-vertex graph that is either a complete graph or a star graph. As shown in \cite{hein2006entanglement}, both the star and complete graphs are equivalent to the multi-qubit GHZ state under local operations.

The $ n $-qubit GHZ state is expressed as


\begin{equation}
    \ket{GHZ_n} = \frac{\ket{0}^{\otimes n} + \ket{1}^{\otimes n}}{\sqrt{2}}.
\end{equation}

% Let $ \rho_{GHZ} = \ket{GHZ_n}\bra{GHZ_n} $, and consider a pair of vertices $ u $ and $ v $ in the graph $ G $. On taking the partial trace over all vertices of the graph except for $ u $ and $ v $, the resulting reduced density matrix, denoted $ \rho^{u,v} $, is given by 

% $$
% \rho^{u,v} = \frac{\ket{00}\bra{00}}{2} + \frac{\ket{11}\bra{11}}{2}.
% $$
% Similarly, the reduced density matrix for any single vertex $ v $ in the graph $ G $, denoted $ \rho^v $, is 

% $$
% \rho^v = \frac{\ket{0}\bra{0}}{2} + \frac{\ket{1}\bra{1}}{2}.
% $$

When performing the partial trace over any subsystem of a GHZ state, the resulting reduced density matrix has a spectrum of $0.5$ with multiplicity $2$ and the remaining eigenvalues are 0. Using Eq. \eqref{eq:linear_entropy} we can compute the linear entropy of any reduced density matrix $\rho_A$ as 
\begin{align}
    S_2(A) &= 1 - \trace{\rho_A^2} \\
    &= 1 - \sum_{i} \lambda(i)^2 \\
    &= 1 - 2 \cdot \left(\frac{1}{2} \right)^2 = 1/2.
\end{align}
This holds for all proper subsets \( A \subset S \). The linear entropy of any 1 or 2 qubit subsystem is \( 0.5 \). Specifically, for any qubit pair \( u, v \), we have \( S_2(u) = S_2(v) = S_2(u, v) = 0.5 \). The 2-deformed correlation for any qubit subsystem is then computed using Eq. \eqref{eq:correlation_function} as 
\begin{equation}
C_2(u, v) = S_2(u) + S_2(v) - S_2(u, v) = 2 \cdot 0.5 - 0.5 = 0.5.
\end{equation}

% , we obtain that for any pair of vertices $ u, v $ in the graph, the linear entropy for each individual vertex, $ S_2(u) $ and $ S_2(v) $, as well as for the pair $ S_2(u, v) $, is $ 0.5 $. Substituting these entropy values into the correlation function formula in equation \eqref{eq:correlation_function}, we calculate the 2-deformed correlation between the vertex pair $ (u, v) $,
% \begin{equation}
% C_2(u, v) = S_2(u) + S_2(v) - S_2(u, v) = 2 \cdot 0.5 - 0.5 = 0.5.
% \end{equation}

Since for every qubit pair $u, v$, $C_2(u, v) = 0.5$, we can apply Lemma \ref{lemma:correlation_function_value_relation_with_topological_graph}
and conclude that the corresponding topological structure $ \mathcal{X} $ consists of $ n $ disconnected vertices for $ 0 \leq \epsilon < 0.5 $, and it forms a complete graph at $ \epsilon = 0.5 $.
% To determine the 2-deformed correlation for the vertex pair $ (u, v) $, we compute $ C_2(u, v) $ as follows:

% $$
% C_2(u, v) = S_2(u) + S_2(v) - S_2(u, v) = 0.5 \cdot 2 - 0.5 = 0.5.
% $$

% Given that for any two qubits $ u $ and $ v $ in a GHZ state, $ C_2(u, v) = 0.5 $, the corresponding vertex pair in the topological space $ \mathcal{X} $ remains disconnected for $ 0 \leq \epsilon < 0.5 $. At $ \epsilon = 0.5 $, an edge is established between the vertices. As this occurs for every pair of vertices, the topological structure is disconnected for $ 0 \leq \epsilon < 0.5 $ and forms a complete graph at $ \epsilon = 0.5 $.

\textbf{Proof in backward direction:}
Given a topological structure $ \mathcal{X} $ with $ n $ disconnected vertices for $ 0 \leq \epsilon < 0.5 $, and which forms a complete graph at $ \epsilon = 0.5 $, we refer to Lemma \eqref{lemma:correlation_function_value_relation_with_topological_graph}. From this, we conclude that the 2-deformed correlation function for any pair of vertices $ (u, v) $ in $V$ is $ C_2(u, v) = 0.5 $. Given that every vertex pair $(u, v)$ in graph $G$ with no isolated vertex, $C_2(u, v) = 0.5$, we will prove that the corresponding graph is a star or a complete graph.

There are 2 cases we consider here 
\begin{itemize}
    \item \textbf{Case 1 :} $\exists u \in V$ such that $deg(u) = 1$ \\
    Assume vertex $ u $ has degree 1, with $ N(u) = \{w\} $ for some $ w \in V $. Given that the 2-deformed correlation $ C_2(u, v) = 0.5 $ for any vertex $ v \in V \setminus \{u, w\} $, and applying proposition \eqref{prop:correlation_function_relation_with_graph_structure}, we conclude that this is only possible if $ N(v) \setminus \{u\} = N(u) \setminus \{v\} \neq \emptyset $. Since $ N(u) \setminus \{v\} = \{w\} $, it follows that $ N(v) \setminus \{u\} = \{w\} $, and thus $ N(v) = \{w\} $. Therefore, for all $ v \in V \setminus \{w\} $, we have $ N(v) = \{w\} $ and consequently G is a star graph.
     \item \textbf{Case 2 :} $\forall u \in V$ such that $deg(u) > 1$ \\
    Since the degree of a vertex can never be 1, by proposition \eqref{prop:correlation_function_relation_with_graph_structure}, we have $ C_2(u, v) = 0.5 $ for any pair of vertices $ u, v \in G $ if and only if $ N(u) \setminus \{v\} = N(v) \setminus \{u\} \neq \emptyset $. This implies that for any pair of vertices $ u, v \in V $, $ N(u) \setminus \{v\} = N(v) \setminus \{u\} \neq \emptyset $. Applying  proposition \ref{prop:complete_graph_iff_neighbor_set_condition}, we conclude that $ G $ must be a complete graph.
\end{itemize}
\end{proof}






\begin{theorem}

There are $ n $ 0-dimensional holes for $ 0 \leq \epsilon < 0.5 $. At $ \epsilon = 0.5 $, one 0-dimensional hole and $ \frac{(n-1)(n-2)}{2} $ 1-dimensional holes form if and only if topological space $\mathcal{X}$ has n disconnected vertices between  $ 0 \leq \epsilon < 0.5 $ and forms a complete graph at  $ \epsilon = 0.5$.
\end{theorem}
\begin{proof}
\textbf{Proof in Forward direction}
Assume that for $ 0 \leq \epsilon < 0.5 $, there are $ n $ 0-dimensional holes, and at $ \epsilon = 0.5 $, there is one 0-dimensional hole and $ \frac{(n-1)(n-2)}{2} $ 1-dimensional holes.

For $ 0 \leq \epsilon < 0.5 $, the $ n $ 0-dimensional holes correspond to $ n $ disconnected vertices in the topological space. At $ \epsilon = 0.5 $, the topological space has one 0-dimensional hole, indicating a single connected component ($ c = 1 $). At this value of the filtration parameter, the space consists of $ n $ vertices, 1 connected component, and $ \frac{(n-1)(n-2)}{2} $ 1-dimensional holes, which correspond to the dimension of the cycle basis.

The dimension of the cycle basis is given in \cite{hage1996island} and is computed using the number of edges, vertices, and connected components
\begin{equation}
\text{Cycle basis dimension} = m - n + c,
\end{equation}
where $ m $ is the number of edges, $ n $ is the number of vertices, and $ c = 1 $ is the number of connected components. Substituting the values:
\begin{equation}
\frac{(n-1)(n-2)}{2} = m - n + 1
\end{equation}
Solving for $ m $, we find:
\begin{equation}
m = \frac{n(n-1)}{2}
\end{equation}
Therefore, the topological structure $ \mathcal{X} $ is a complete graph at $\epsilon = 0.5$ and $n$ isolated vertices vertices at $ 0 \leq \epsilon < 0.5 $

\textbf{Proof in Backward direction}
Assume the topological structure has $ n $ disconnected vertices for $ 0 \leq \epsilon < 0.5 $, and forms a complete graph at $ \epsilon = 0.5 $. For $ 0 \leq \epsilon < 0.5 $, the $ n $ disconnected vertices correspond to $ n $ 0-dimensional holes, as the number of connected components equals the number of 0-dimensional holes. At $ \epsilon = 0.5 $, the space becomes a complete graph, which is connected, so there is exactly one 0-dimensional hole.

The number of 1-dimensional holes corresponds to the dimension of the cycle basis. For a complete graph with $ n $ vertices, the number of edges is $ \frac{n(n-1)}{2} $, and there is 1 connected component. 

% The dimension of the cycle basis is given by the formula $ m - n + c $, where $ m $ is the number of edges, $ n $ is the number of vertices, and $ c $ is the number of connected components. 

Substituting the values in the equation for the dimension of the cycle basis, we get:

\begin{equation}
\frac{n(n-1)}{2} - n + 1 = \frac{(n-1)(n-2)}{2}
\end{equation}


Thus, at $ \epsilon = 0.5 $, there is a single 0-dimensional hole and $ \frac{(n-1)(n-2)}{2} $ 1-dimensional holes. Hence, the proposition follows in the backward direction.
\end{proof}

\begin{corollary}
Let $\rho = \ket{\psi}\bra{\psi}$ be a pure multipartite quantum state in Hilbert space $(\mathbb{C}^2)^{\otimes n}$. We propose that $\rho$ is a local unitary equivalent $n$ qubit GHZ state if and only if the linear entropy of every 2 qubit subsystem of $\rho$ is 0.5.
\end{corollary}

\begin{theorem}
    Let $\rho = \ket{\psi}\bra{\psi}$ be a pure multipartite graph quantum state in Hilbert space $(\mathbb{C}^2)^{\otimes n}$. The quantum system $\rho$ generates $n$ 0-dimensional holes for $0 \leq \epsilon < 0.5$ and at $\epsilon = 0.5$, one 0-dimensional holes and $\frac{(n-1)(n-2)}{2}$ 1-dimensional hole if and only if the graph associated with $\rho$ is a star or complete graph.
\end{theorem}


% \subsection*{Conclusion}
% Using Theorem 3.4.1 and Theorem 3.4.3, we can conclude that
% \\
% \\
% A n-GHZ state if there are n 0-dimensional holes for $0 \leq \epsilon < 0.5$. At $\epsilon = 0.5$, one 0-dimensional hole
% and $\frac{(n-1)(n-2)}{2}$ 1-dimensional hole
% \\
% \\
% Using Theorem 3.4.2 and Theorem 3.4.3, we can conclude that
% \\
% \\
% Graph G is a complete graph or star graph if and only if there are n 0-dimensional holes for $0 \leq \epsilon < 0.5$. At $\epsilon = 0.5$, one 0-dimensional hole
% and $\frac{(n-1)(n-2)}{2}$ 1-dimensional hole

\bibliographystyle{plain}
\bibliography{reference}
\end{document}